ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-25 pyked.tex
Add first usage example
The Python bit is untested, probably should be tested before publication

%====================================================================
\section{Conclusions and future work}
%
\todo[inline]{both to do}

>>>>

The following usage examples provide a guide to the use of \pk{}. They are by no
means an exhaustive treatement, and are meant to demonstrate the basic
capabilities of the software.

\subsection{RCM modeling with varying reactor volume}\label{sec:rcm-modeling}

The \ck{} file that will be used in this example can be found in the
\python|tests| directory of the PyKED repository,
\url{https://github.com/pr-omethe-us/PyKED/blob/master/pyked/tests/testfile_rcm.yaml}.
Examining that file, we find the first section specifies the information about
the \ck{} file itself
%
\begin{minted}{yaml}
file-author:
  name: Kyle E Niemeyer
  ORCID: 0000-0003-4425-7097
file-version: (1, 0)
chemked-version: 0.0.1
fake-key: 0 # Again here because Atom's syntax highlighting is busted :(
\end{minted}
%
Then, we find the information regarding the article in the literature from which
this data was taken. In this case, the data point is from the work of \textcite{Mittal2006a}:
%
\begin{minted}{yaml}
reference:
  doi: 10.1002/kin.20180
  authors:
    - name: Gaurav Mittal
    - name: Chih-Jen Sung
      ORCID: 0000-0003-2046-8076
    - name: Richard A Yetter
  journal: International Journal of Chemical Kinetics
  year: 2006
  volume: 38
  pages: 516-529
  detail: Fig. 6, open circle
experiment-type: ignition delay
apparatus:
  kind: rapid compression machine
  institution: Case Western Reserve University
  facility: CWRU RCM
  fake-key: 0 # Again here because Atom's syntax highlighting is busted :(
\end{minted}

Finally, there is just a single datapoint in this file, which codes the ignition
delay for the experiment, the mixture composition, the initial temperature,
pressure,
%
\begin{minted}{yaml}
datapoints:
  - temperature: 297.4 kelvin
    ignition-delay: 1.0 ms
    pressure: 958.0 torr
    composition:
      - species-name: H2
        InChI: 1S/H2/h1H
        mole-fraction: 0.12500
      - species-name: O2
        InChI: 1S/O2/c1-2
        mole-fraction: 0.06250
      - species-name: N2
        InChI: 1S/N2/c1-2
        mole-fraction: 0.18125
      - species-name: Ar
        InChI: 1S/Ar
        mole-fraction: 0.63125
    ignition-type:
      target: pressure
      type: d/dt max
    compression-time: 38.0 ms
    volume-history:
      time:
        units: s
        column: 0
      volume:
        units: cm3
        column: 1
      values:
        - [0.00E+000, 5.47669375000E+002]
        - [1.00E-003, 5.46608789894E+002]
        - [2.00E-003, 5.43427034574E+002]
        - [3.00E-003, 5.38124109043E+002]
        - 0 # Dammit Atom
        ...
\end{minted}

The values for the \yaml|volume-history| are truncated to save space. The user
can load this file into \pk{} and run a simulation in Cantera with the following
code:

\begin{minted}{python}
import cantera as ct
from pyked import ChemKED

ck = ChemKED('testfile_rcm.yaml')
dp = ck.datapoints[0]

T_0 = dp.temperature.to('K').magnitude
P_0 = dp.pressure.to('Pa').magnitude
X_0 = dp.get_cantera_mole_fraction()

gas = ct.Solution('h2-co-mechanism.cti')
gas.TPX = T_0, P_0, X_0

reac = ct.IdealGasReactor(gas)
env = ct.Reservoir(ct.Solution('air.xml'))

time = dp.volume_history.time
volume = dp.volume_history.volume
ct.Wall(reac, env, velocity=VolumeProfile(time=time, volume=volume))

netw = ct.ReactorNet([reac])
while netw.time < 0.05:
    netw.step()

\end{minted}
%====================================================================
\section{Conclusions and future work}
%
\todo[inline]{both to do}
